Test data

### 2022-07-21 Shiny/Test/Test data.Rmd
Plotly caption function test.

"Note: not all values are denominated in the same currency"
```

@@

### Expenses
```{r}
kreft_excel |> 
  transmute(
    Year = as.factor(year),
    Other = expenses_other,
    Administrative = expenses_administrative,
    Fundraising = expenses_fundraising,
    `Program services` = expenses_program_services
  ) |> 
  pivot_longer(c(Other:`Program services`), names_to = "Expenses") |> 
  mutate(
    Expenses = ordered(Expenses, levels =
                         c("Program services", "Administrative",
                         "Fundraising", "Other")) 
  ) |> 
  ggplot(aes(Year, value, fill = Expenses)) +
  geom_col() +
  coord_flip() +
  scale_y_continuous(labels = label_dollar()) +
  scale_fill_met_d("Troy")

>>>>

"Note: not all values are denominated in the same currency"

# bad test
    mutate(
    valutakode = ifelse(year == 2019, "USD", valutakode)
  ) |>
```

@@

### Expenses
```{r}
expenses_plot <- kreft_excel |> 
  transmute(
    Year = as.factor(year),
    Other = expenses_other,
    Administrative = expenses_administrative,
    Fundraising = expenses_fundraising,
    `Program services` = expenses_program_services
  ) |> 
  pivot_longer(c(Other:`Program services`), names_to = "Expenses") |> 
  mutate(
    Expenses = ordered(Expenses, levels =
                         c("Program services", "Administrative",
                         "Fundraising", "Other")) 
  ) |> 
  ggplot(aes(Year, value, fill = Expenses)) +
  geom_col() +
  coord_flip() +
  scale_y_continuous(labels = label_dollar()) +
  scale_fill_met_d("Troy")

ggplotly(expenses_plot) |>
      layout(
        annotations =
          list(
            x = 1, y = -0.1, text = "currency_caption()",
            showarrow = F, xref = "paper", yref = "paper",
            xanchor = "right", yanchor = "auto", xshift = 0, yshift = 0,
            font = list(size = 11)
          )
      )

plotlylayout <- function()({
  list(
            x = 1, y = -0.1, text = "currency_caption()",
            showarrow = F, xref = "paper", yref = "paper",
            xanchor = "right", yanchor = "auto", xshift = 0, yshift = 0,
            font = list(size = 11)
          )
})

ggplotly(expenses_plot) |> 
layout(annotations = plotlylayout())
